### 2025-11-05 YEAR2/AER210_LectureNotes/main.tex
nov 5

\subsection{Basic Eqaution for Preessure Fiekd}
\begin{theorem}[Hydrostatic Pressure Equation]
    In a fluid at rest, the pressure gradient is related to the body forces acting on the fluid. Mathematically, we write:
    \begin{equation}
        \nabla P = \rho \vec{g}
    \end{equation}
    where \(\nabla P\) is the pressure gradient, \(\rho\) is the fluid density, and \(\vec{g}\) is the acceleration due to gravity. 
\end{theorem}
\end{document}

>>>>

\subsection{Basic Eqaution for Preessure Fiekd}
\begin{theorem}[Hydrostatic Pressure Equation]
    In a fluid at rest, the pressure gradient is related to the body forces acting on the fluid. Mathematically, we write:
    \begin{equation}
        \nabla P = \rho \vec{g}
    \end{equation}
    where \(\nabla P\) is the pressure gradient, \(\rho\) is the fluid density, and \(\vec{g}\) is the acceleration due to gravity. 
\end{theorem}

\begin{definition}[Hydrodatic Force on a Submerged Surface]
    The hydrostatic force \(F\) acting on a submerged surface \(S\) is given by:
    \begin{equation}
        F = \iint_S P \, dA
    \end{equation}
    where \(P\) is the pressure at each point on the surface and \(dA\) is the infinitesimal area element of the surface.

    The point of application of the hydrostatic force, known as the center of pressure, can be determined by finding the centroid of the pressure distribution on the surface.
\end{definition}

\begin{definition}[Pressure Prism]
    A pressure prism is a graphical representation of the pressure distribution on a submerged surface. It is typically used to visualize the variation of pressure with depth in a fluid. The height of the prism at any point on the surface corresponds to the pressure at that point, and the area of the prism represents the total hydrostatic force acting on the surface.
\end{definition}

\begin{example}[Pressure Prsim]
    Cosndier a rectangular dam with a width \(b\) and a height \(h\). The dam is submerged in water, and we want to calculate the hydrostatic force acting on the dam. The pressure at a depth \(z\) below the water surface is given by:
    \[P(z) = \rho g z\]
    where \(\rho\) is the density of water and \(g\) is the acceleration due to gravity. The average pressure on the dam can be calculated as:
    \[P_{avg} = \frac{\rho g h}{2}\]
    The hydrostatic force acting on the dam is then given by:
    \[F = P_{avg} \cdot A = \frac{\rho g h}{2} \cdot (b \cdot h) = \frac{1}{2} \rho g b h^2\]
    where \(A = b \cdot h\) is the area of the dam. To visulzied this, we can draw a pressure prism in the \textit{prssure-area space} where the base of the prism is the area of the dam and the height of the prism is the average pressure acting on the dam. Then, we can condlue that the magnitude of the hydrostatic force is equal to the volume of the pressure prism.

    The centroid of the pressure prism can be found to determine the point of application of the hydrostatic force. For a rectangular dam, the centroid is located at a depth of \(\frac{h}{3}\) from the base of the dam.

    \textbf{Important} This method is \textbf{only valid for planar surfaces}.
\end{example}

\begin{definition}[Determining Centroid]
 Recall, the centroid of a shape with multiple geometries is calculated by: 
\begin{equation}
\bar{y} = \frac{\sum_i V_i  y_i}{\sum_i V_i}
\end{equation}
\end{definition}

\paragraph{Note} Effect of atmospheric pressure: In most hydrostatic problems, the effect of atmospheric pressure is neglected because it acts uniformly on all surfaces and does not contribute to the net force on submerged surfaces. However, if the surface is exposed to the atmosphere, the atmospheric pressure must be considered in addition to the hydrostatic pressure.

\end{document}

### 2025-11-05 YEAR2/ECE253_LectureNotes/main.tex
nov 5

    In RISC-V architecture, there are 32 general-purpose registers (x0 to x31), each 32 bits wide in the RV32I variant. The register x0 is hardwired to zero and cannot be modified. The other registers can be used for various purposes, such as holding function arguments, return values, and temporary data.
\end{definition}
\end{document}

>>>>

\begin{definition}[\texttt{lw} and \texttt{la} Instructions]
    The \verb|lw| (load word) instruction is used to load a 32-bit word from memory into a register. The syntax for the \verb|lw| instruction is as follows:
    \begin{verbatim}
    lw rX, offset(rY)
    \end{verbatim}
    This instruction loads the word located at the memory address calculated by adding the value in register \verb|rY| and the signed immediate \verb|offset| into register \verb|rX|.

    The \verb|la| (load address) instruction is used to load the address of a label or variable into a register. The syntax for the \verb|la| instruction is as follows:
    \begin{verbatim}
    la rX, LABEL
    \end{verbatim}
    This instruction loads the address of the label or variable \verb|LABEL| into register \verb|rX|.
\end{definition}

\begin{example}[RISC-V Assembly Code - Rolling Sum]
    Consider the following C code that uses that performs a rolling sum using pointers of a 4 words array:
    \begin{verbatim}
    void rolling_sum(int *arr, int n) {
        int sum = 0;
        for (int i = 0; i < n; i++) {
            sum += arr[i];
        }
        return sum;
    }

    int main() {
        int LIST[4] = {1, 2, 3, 4};
        int result = rolling_sum(LIST, 4);
        return 0;
    }
    \end{verbatim}
    The equivalent RISC-V assembly code would be:
    \begin{verbatim}
    .data
    LIST: .word 1, 2, 3, 4  # Example array

    .global _start # label is visible to other files
    .text # where the instructions are located

    _start:
        la s1, LIST   # Load address of LIST into s1
        lw s2, 0(s1)  # Load first element of LIST into s2
        lw s3, 4(s1)  # Load second element of LIST into s3
        add s2 , s2, s3 # sum = arr[0] + arr[1]
        lw s3, 8(s1)  # Load third element of LIST into s3
        add s2 , s2, s3 # sum += arr[2]
        lw s3, 12(s1)  # Load fourth element of LIST into s3
        add s2 , s2, s3 # sum += arr[3]
        # sum is now in s2
    END: ebreak # we use ebreak to end the program, to transfer control to the simulator
    \end{verbatim}
\end{example}

\begin{definition}[Logic Instructions]
    Logic instructions are a type of assembly language instruction that perform bitwise operations on binary data. These instructions typically operate on values stored in registers or memory locations and can include operations such as AND, OR, NOT, and XOR.

    For example, consider the following high-level code:
    \begin{verbatim}
    int a = b & c; // bitwise AND
    int a = b | c; // bitwise OR
    int a = b ^ c; // bitwise XOR
    int a = ~b;    // bitwise NOT
    \end{verbatim}

    The equivalent assembly code using RISC-V instructions would be:
    \begin{verbatim}
    AND rA, rB, rC  # rA = rB & rC
    OR  rA, rB, rC  # rA = rB | rC
    XOR rA, rB, rC  # rA = rB ^ rC
    NOT rA, rB      # rA = ~rB; Pseudo-instruction,
    # use XORI rA, rB, -1, since -1 = 0xFFFFFFFF
    \end{verbatim}
    where \verb|rA| occupies the destination operand, while \verb|rB| and \verb|rC| are the source operands.

    We can also use the immediate values as operands:
    \begin{verbatim}
    ANDI rA, rB, #D  # rA = rB & D
    ORI  rA, rB, #D  # rA = rB | D
    XORI rA, rB, #D  # rA = rB ^ D
    \end{verbatim}
\end{definition}

\begin{definition}[Shift Instructions]
    Shift instructions are a type of assembly language instruction that perform bitwise shift operations on binary data. These instructions typically operate on values stored in registers and can include operations such as logical shift left (LSL), logical shift right (LSR), and arithmetic shift right (ASR).

    For example, consider the following high-level code:
    \begin{verbatim}
    int a = b << n; // logical shift left
    int a = b >> n; // logical shift right
    int a = b >> n; // arithmetic shift right
    \end{verbatim}

    The equivalent assembly code using RISC-V instructions would be:
    \begin{verbatim}
    SLL rA, rB, rC  # rA = rB << rC (logical shift left)
    SRL rA, rB, rC  # rA = rB >> rC (logical shift right)
    SRA rA, rB, rC  # rA = rB >> rC (arithmetic shift right)
    \end{verbatim}
    where \verb|rA| occupies the destination operand, while \verb|rB| is the source operand and \verb|rC| specifies the number of bits to shift.

    The arithmetic shift right (ASR) preserves the sign bit (the most significant bit) when shifting right, which is important for signed integers. In contrast, the logical shift right (LSR) fills the vacated bits with zeros, regardless of the sign of the number.

    To multiply or divide by powers of two, we can use shift instructions:
    \begin{verbatim}
    SLA rA, rB, #D  # rA = rB * 2^D (multiply by 2^D)
    SRA rA, rB, #D  # rA = rB / 2^D (divide by 2^D, if it is divisable)
    \end{verbatim}

    We can also use immediate values as operands:
    \begin{verbatim}
    SLLI rA, rB, #D  # rA = rB << D (logical shift left)
    SRLI rA, rB, #D  # rA = rB >> D (logical shift right)
    SRAI rA, rB, #D  # rA = rB >> D (arithmetic shift right)
    \end{verbatim}
\end{definition}

\begin{definition}[Accessing a byte and half word]
    In RISC-V, we can access individual bytes and half-words (16 bits) using specific load and store instructions.

    To load a byte from memory into a register, we use the \verb|lb| (load byte) instruction:
    \begin{verbatim}
    lb rX, offset(rY)
    \end{verbatim}
    This instruction loads the byte located at the memory address calculated by adding the value in register \verb|rY| and the signed immediate \verb|offset| into register \verb|rX|. The loaded byte is sign-extended to fill the 32-bit register.

    To load a half-word from memory into a register, we use the \verb|lh| (load half-word) instruction:
    \begin{verbatim}
    lh rX, offset(rY)
    \end{verbatim}
    This instruction loads the half-word located at the memory address calculated by adding the value in register \verb|rY| and the signed immediate \verb|offset| into register \verb|rX|. The loaded half-word is sign-extended to fill the 32-bit register.

    Similarly, to store a byte from a register into memory, we use the \verb|sb| (store byte) instruction:
    \begin{verbatim}
    sb rX, offset(rY)
    \end{verbatim}
    This instruction stores the least significant byte of register \verb|rX| into the memory address calculated by adding the value in register \verb|rY| and the signed immediate \verb|offset|.

    To store a half-word from a register into memory, we use the \verb|sh| (store half-word) instruction:
    \begin{verbatim}
    sh rX, offset(rY)
    \end{verbatim}
    This instruction stores the least significant half-word of register \verb|rX| into the memory address calculated by adding the value in register \verb|rY| and the signed immediate \verb|offset|.

\end{definition}
\end{document}

### 2025-11-05 YEAR2/MAT292_LectureNotes/main.tex
nov 5

@@

>>>>

\begin{definition}[General Planar System of ODEs]
    Consider the general planar system of ODEs:
    $$
    X' = P(t)X + G(t)
    $$
    where \( X = \begin{bmatrix} x \\ y \end{bmatrix} \), \( P(t) = \begin{bmatrix} p_{11}(t) & p_{12}(t) \\ p_{21}(t) & p_{22}(t) \end{bmatrix} \), and \( G(t) = \begin{bmatrix} g_1(t) \\ g_2(t) \end{bmatrix} \). The system is called:
    \begin{itemize}
        \item \textbf{Homogeneous} if \( G(t) = 0 \) for all \( t \).
        \item \textbf{Non-homogeneous} if \( G(t) \neq 0 \) for some \( t \).
        \item \textbf{Autonomous} if \( P(t) \) and \( G(t) \) are constant matrices/vectors.
        \item \textbf{Non-autonomous} if \( P(t) \) and/or \( G(t) \) are functions of \( t \).
    \end{itemize}
\end{definition}

\begin{definition}[Method to Solve General Planar System of ODEs]
    To solve the general planar system of ODEs, we can translate the system into a higher-dimensional homogeneous system by translating the fixed point to the origin. Let \( X^* \) be the fixed point of the system, then we define a new variable \( Y = X - X^* \). The system becomes:
    $$Y' = P(t)Y
$$
    We can then solve this homogeneous system using methods for linear systems of ODEs.
\end{definition}

\begin{example}
    Consider the system of ODEs:
    $$
    \textbf{x}' = \begin{bmatrix} 2 & 3 \\ 1 & 4
    \end{bmatrix}\textbf{x} + \begin{bmatrix} 5 \\ 6
    \end{bmatrix}
    $$
    We find the fixed point by solving:
    $$
    A\textbf{x}^* + \textbf{b} = 0 \implies \begin{bmatrix} 2 & 3 \\ 1 & 4
    \end{bmatrix}\textbf{x}^* = -\begin{bmatrix} 5 \\ 6
    \end{bmatrix}
    $$
    Solving this, we find:
    $$
    \textbf{x}^* = \begin{bmatrix} -3 \\ 2
    \end{bmatrix}
    $$
    We define a new variable \( \textbf{y} = \textbf{x} - \textbf{x}^* \), then the system becomes:
    $$
    \textbf{y}' = \begin{bmatrix} 2 & 3 \\ 1 & 4
    \end{bmatrix}\textbf{y}
    $$
    We can then solve this homogeneous system using methods for linear systems of ODEs.
\end{example}

@@

We want to formalize the two methods of finding particular solutions: undetermined coefficients and variation of parameters.

\begin{theorem}[Method of Undetermined Coefficients]
    The method of undetermined coefficients is a technique used to find a particular solution to a non-homogeneous linear differential equation with constant coefficients. For a second-order ODE of the form:
    $$y'' + p y' + q y = g(t)$$
    where \( g(t) \) is a linear combination of functions such as polynomials, exponentials, sines, and cosines, we can assume a particular solution \( y_p(t) \) of the same form as \( g(t) \), but with undetermined coefficients. The steps to apply this method are as follows:
    \begin{enumerate}
        \item Identify the form of \( g(t) \).
        \item Assume a particular solution \( y_p(t) \) with undetermined coefficients based on the form of \( g(t) \).
        \item Substitute \( y_p(t) \) into the left-hand side of the differential equation.
        \item Solve for the undetermined coefficients by equating the resulting expression to \( g(t) \).
    \end{enumerate}
    This method is effective when \( g(t) \) is composed of functions whose derivatives are similar in form to the original function.
\end{theorem}

\begin{example}
    Consider the ODE:
    $$y'' - 3y' + 2y = e^{2t} + \sin(t)$$
    The corresponding homogeneous equation is:
    $$y'' - 3y' + 2y = 0$$
    The characteristic equation is:
    $$r^2 - 3r + 2 = 0$$
    Solving this gives the roots \( r_1 = 2 \) and \( r_2 = 1 \). Thus, the general solution of the homogeneous equation is:
    $$y_h(t) = C_1 e^{2t} + C_2 e^{t}$$
    where \( C_1 \) and \( C_2 \) are constants determined by initial conditions.

    Next, we find a particular solution for each term on the right-hand side of the inhomogeneous equation. For the term \( e^{2t} \), since \( e^{2t} \) is already a solution of the homogeneous equation, we assume a particular solution of the form \( y_{p_1}(t) = At e^{2t} \). Substituting this into the left-hand side of the ODE gives:
    \begin{align*}
        y_{p_1}'' - 3y_{p_1}' + 2y_{p_1} &= (4At + 4A)e^{2t} - 3(2At + A)e^{2t} + 2At e^{2t} \\
        &= (4At + 4A - 6At - 3A + 2At)e^{2t} \\
        &= (0At + A)e^{2t} \\
        &= Ae^{2t}
    \end{align*}

    Setting this equal to \( e^{2t} \) gives:
    $$Ae^{2t} = e^{2t} \implies A = 1$$
    Thus, we have:
    $$y_{p_1}(t) = t e^{2t}$$

    For the term \( \sin(t) \), we can assume a particular solution of the form \( y_{p_2}(t) = B \cos(t) + C \sin(t) \). Substituting this into the left-hand side of the ODE gives:
    \begin{align*}
        y_{p_2}'' - 3y_{p_2}' + 2y_{p_2} &= -B \cos(t) - C \sin(t) + 3B \sin(t) - 3C \cos(t) + 2B \cos(t) + 2C \sin(t) \\
        &= (B - 3C) \cos(t) + (3B - C) \sin(t)
    \end{align*}
    Setting this equal to \( \sin(t) \) gives the system of equations:
    \begin{align*}
        B - 3C &= 0 \\
        3B - C &= 1
    \end{align*}
    Solving this system gives \( B = \frac{3}{10} \) and \( C = \frac{1}{10} \). Thus, we have:
    $$y_{p_2}(t) = \frac{3}{10} \cos(t) + \frac{1}{10} \sin(t)$$
    Finally, the general solution of the inhomogeneous ODE is:
    $$y(t) = C_1 e^{2t} + C_2 e^{t} + t e^{2t} + \frac{3}{10} \cos(t) + \frac{1}{10} \sin(t)$$
\end{example}

### 2025-11-05 YEAR2/PHY293_LectureNotes/main.tex
nov 5

    First, we calculate the kinetic energy \( K \) of the electrons after being accelerated through the potential difference \( V \):
    $$        
    K = eV = (1.602 \times 10^{-19} \, \text{C})(54 \, \text{V}) = 8.65 \times 10^{-18} \, \text{J} 
    $$
    Next, we calculate the momentum \( p \) of the electrons using the kinetic energy:
    $$        K = \frac{p^2}{2m} \implies p = \sqrt{2mK} $$
    where \( m \) is the mass of the electron (\(9.11 \times 10^{-31} \, \text{kg}\)). Thus,
    $$        p = \sqrt{2(9.11 \times 10^{-31} \, \text{kg})(8.65 \times 10^{-18} \,\text{J})} \approx 1.26 \times 10^{-24} \text{kg·m/s} $$
    Now, we can calculate the de Broglie wavelength \( \lambda \) of the electrons:
    $$        \lambda = \frac{h}{p} = \frac{6.626 \times 10^{-34} \, \text{J·s}}{1.26 \times 10^{-24} \, \text{kg·m/s}} \approx 1.67 \times 10^{-10} \, \text{m} $$
    Finally, we can verify this wavelength using Bragg's law for diffraction:
    $$        n\lambda = 2d \sin \theta $$
    For the first-order maximum (\( n = 1 \)), \( \theta = \frac{180 - 50}{2} = 65^\circ \):
    $$        \lambda = 2(0.091 \times 10^{-9} \, \text{m}) \sin(65^\circ) \approx 1.67 \times 10^{-10} \, \text{m} $$
    This matches our earlier calculation, confirming the de Broglie wavelength of the electrons is approximately \( 1.67 \times 10^{-10} \) meters.
\end{example}
\end{document}

>>>>

    First, we calculate the kinetic energy \( K \) of the electrons after being accelerated through the potential difference \( V \):
    $$        
    K = eV = (1.602 \times 10^{-19} \, \text{C})(54 \, \text{V}) = 8.65 \times 10^{-18} \, \text{J} 
    $$
    Next, we calculate the momentum \( p \) of the electrons using the kinetic energy:
    $$        K = \frac{p^2}{2m} \implies p = \sqrt{2mK} $$
    where \( m \) is the mass of the electron (\(9.11 \times 10^{-31} \, \text{kg}\)). Thus,
    $$        p = \sqrt{2(9.11 \times 10^{-31} \, \text{kg})(8.65 \times 10^{-18} \,\text{J})} \approx 1.26 \times 10^{-24} \text{kg·m/s} $$
    Now, we can calculate the de Broglie wavelength \( \lambda \) of the electrons:
    $$        \lambda = \frac{h}{p} = \frac{6.626 \times 10^{-34} \, \text{J·s}}{1.26 \times 10^{-24} \, \text{kg·m/s}} \approx 1.67 \times 10^{-10} \, \text{m} $$
    Finally, we can verify this wavelength using Bragg's law for diffraction:
    $$        n\lambda = 2d \sin \theta $$
    For the first-order maximum (\( n = 1 \)), \( \theta = \frac{180 - 50}{2} = 65^\circ \):
    $$        \lambda = 2(0.091 \times 10^{-9} \, \text{m}) \sin(65^\circ) \approx 1.67 \times 10^{-10} \, \text{m} $$
    This matches our earlier calculation, confirming the de Broglie wavelength of the electrons is approximately \( 1.67 \times 10^{-10} \) meters.
\end{example}
\subsection{Matter Waves}
\begin{definition}[Matter Wave Function]
    In quantum mechanics, the matter wave function \( \psi(x,t) \) describes the quantum state of a particle. The probability density

    \begin{equation}
        D(x,t) = |\psi(x,t)|^2
    \end{equation}
    gives the likelihood of finding the particle at position \( x \) and time \( t \). The wave function must satisfy the normalization condition:

    \begin{equation}
        \int_{-\infty}^{\infty} |\psi(x,t)|^2 \, dx = 1
    \end{equation}

    The wave function can be expressed as a superposition of plane waves:
\end{definition}

\begin{definition}[Fourier Integtal]
    The foruer transformer of a function $f(x)$ is given by:
    $$
        A(k) = \frac{1}{\sqrt{2\pi}} \int_{-\infty}^{\infty} f(x) e^{-ikx} \, dx
    $$
    The inverse fourier transform is given by:
    $$       
        f(x) = \int _{-\infty}^{\infty} A(k) e^{ikx} \, dk
    $$
\end{definition}
\begin{definition}[Postion and Momentum Space]
    In quantum mechanics, the wave function can be represented in both position space and momentum space. In terms of fourier transformation, $f(x)$ is the wave function in position space, while $A(k)$ is the wave function in momentum space, where \( k \) is related to the momentum \( p \) by \( p = \hbar k \). The probability density in momentum space is given by:
\end{definition}

\begin{definition}[Localization Trade-off]
    In fourier transform, there is a trade-off between the localization of a function in position space and its localization in momentum (wave-number) space. A function that is highly localized in position space will have a broad distribution in momentum space, and vice versa. This is a manifestation of the Heisenberg uncertainty principle. That is, if the position is well-defined, we would see a broad distribution of momenta, and if the momentum is well-defined, we would see a broad distribution of positions.
\end{definition}

\begin{theorem}[Fourier Uncertainty Relation]
    The Fourier uncertainty relation states that the product of the standard deviations of a function in position space and its Fourier transform in momentum space is bounded by a constant:
    \begin{equation}
        \Delta x \Delta k \geq \frac{1}{2}
    \end{equation}
    where \( \Delta x \) is the standard deviation in position space and \( \Delta k \) is the standard deviation in wave-number space:
    $$
        \Delta x = \sqrt{\langle x^2 \rangle - \langle x \rangle^2}, \quad \Delta k = \sqrt{\langle k^2 \rangle - \langle k \rangle^2}
    $$  
    Also, we have, in the time space:
    \begin{equation}
        \Delta t \Delta \omega \geq \frac{1}{2}
    \end{equation}
    where \( \Delta t \) is the standard deviation in time and \( \Delta \omega \) is the standard deviation in angular frequency space.
\end{theorem}

\begin{theorem}[Heisenberg Uncertainty Principle]
    The Heisenberg uncertainty principle states that it is impossible to simultaneously know both the exact position and exact momentum of a particle. The product of the uncertainties in position \( \Delta x \) and momentum \( \Delta p \) is bounded by a constant:
    \begin{equation}
        \Delta x \Delta p \geq \frac{\hbar}{2}
    \end{equation}
    where \( \hbar = \frac{h}{2\pi} \) is the reduced Planck's constant. This principle reflects the fundamental limit on the precision with which certain pairs of physical properties can be known.

\end{theorem}
\begin{proof}
    (Direct Proof) Starting from the Fourier uncertainty relation:
    $$
        \Delta x \Delta k \geq \frac{1}{2}
    $$
    We know that momentum \( p \) is related to wave-number \( k \) by:
    $$
        p = \hbar k
    $$
    Therefore, the uncertainty in momentum \( \Delta p \) can be expressed in terms of the uncertainty in wave-number \( \Delta k \):
    $$
        \Delta p = \hbar \Delta k
    $$
    Substituting this into the Fourier uncertainty relation gives:
    $$
        \Delta x \left( \frac{\Delta p}{\hbar} \right) \geq \frac{1}{2}
    $$
    Multiplying both sides by \( \hbar \) yields:
    $$
        \Delta x \Delta p \geq \frac{\hbar}{2}
    $$
    This completes the proof of the Heisenberg uncertainty principle.
\end{proof}

\begin{definition}[Time-Energy Uncertainty Principle]
    The time-energy uncertainty principle states that there is a fundamental limit to the precision with which energy and time can be simultaneously known. The product of the uncertainties in wave angular frequency \( \Delta \omega \) and time \( \Delta t \) is bounded by a constant:
    \begin{equation}
        \Delta \omega \Delta t \geq \frac{\hbar}{2}
    \end{equation}
    This principle implies that if a system exists in a state for a very short time, there is a corresponding uncertainty in its energy.
\end{definition}
\begin{proof}
    (Sketch) Starting from the Fourier uncertainty relation in the time domain, we use the same reasoning as in the position-momentum case. 
\end{proof}
\begin{definition}[Hilbert Space]
    A Hilbert space is a complete inner product space that provides the mathematical framework for quantum mechanics. it is the space cotnaining all physically allowed wave function that are:
    \begin{itemize}
        \item Complex, continuous, and normalizable.
        \item Can be added together and multiplied by complex scalars (i.e., it is a vector space).
        \item Equipped with an inner product that allows for the calculation of probabilities and expectation values.
    \end{itemize}
\end{definition}
\begin{theorem}[From fourier to Hilbert Space]
    Every wave function $\psi(x,t)$ can be represented as a vector in a Hilbert space. Where each of the basis vectors corresponds to a specific state of the system, such as a position eigenstate or momentum eigenstate. The inner product in this space allows us to calculate probabilities and expectation values of observables. Of coruse, it must satisfy the normalization condition:
    $$        \int_{-\infty}^{\infty} |\psi(x,t)|^2 \, dx = 1
    $$
    This idea will be explored further in the next chapters.
\end{theorem}

\end{document}
